The Influence of Connectivity on Dung Beetle Communities

### 2025-07-25 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
scale discussion

Finally, it is important to emphasize that while dung beetles are capable of long distance flight and detecting dung at distances of over 50 meters [@WOS:000707546700001], the results I observed are likely the result of a mismatch between the spatial scale of the experimental replicates and dung beetle movement. Put another way, some beetles were almost certainly drawn by the dung used in baits from the matrix into the plots. If this were a big effect we'd expect all plots to be similar to the matrix, or at least to each other. The fact that rectangular are lower suggests that some sort of landscape effect is apparent, likely related to habitat edge since connected and winged patches were the most similar.

>>>>

Finally, it is important to emphasize that while dung beetles are capable of long distance flight and detecting dung at distances of over 50 meters [@WOS:000707546700001], the results I observed are likely the result of a mismatch between the spatial scale of the experimental replicates and dung beetle movement. Put another way, some beetles were almost certainly drawn by the dung used in baits from the matrix into the plots. If this were an overarching effect we'd expect all plots to be similar to the matrix, or at least to each other. The fact that rectangular are have lower abundance suggests that some sort of landscape effect is apparent, likely related to habitat edge since connected and winged patches were the most similar. To remedy this issue any future work in this site should either focus solely on dung beetles with less dispersal ability or consider mark release recapture sampling in order to better isolate movements within and between patches.
